Plots for Latent Hawkes Paper

### 2021-06-28 output_scripts/Paper_Plots.Rmd
working on redoing the paper plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "paper_figure/",
                      dev = 'png', fig.height = 4.5, fig.width = 7,
                      warning = FALSE)

slides_plots <- FALSE
extra_plots <- FALSE
current_cohort <- 5

@@

library(here)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = '-march=corei7 -mtune=corei7')
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir,'naiveRankHierarchy.R',sep = ""))
source(paste(func_dir,'expertRankHierarchy.R',sep = ""))
source(paste(func_dir,'cleanData.R',sep = "")) 
source(paste(func_dir,'prepareDataStan.R',sep = "")) 
source(paste(func_dir,'inferLatentMmhp.R',sep = ""))
source(paste(func_dir,'plotUtil.R',sep = "")) 
source(paste(func_dir,'mmhp.R',sep = ""))
source(paste(func_dir,'uniHawkes.R',sep = ""))
source(paste(func_dir,'simulatePrediction.R',sep = ""))
source(paste(func_dir,'myGlicko.R',sep = ""))
source(paste(func_dir,'matrixPlotParameter.R',sep = ""))
source(paste(func_dir,'residualStructureScore.R',sep = ""))
source(paste(func_dir,'drawIntensity.R',sep =""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

cohort_names <- paste("cohort",c(9,10,12,15,16,17,18,37,38,45),sep='')
cohort_short_names <- paste("C",c(9,10,12,15,16,17,18,37,38,45),sep='')
cut_off <- 3
mice_number <- 12

```{r load rankings,echo=FALSE,include=FALSE,results='hide',cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(curr_cohort in fit_cohorts){
  naive_rank_10[[curr_cohort]] <-
    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <-
    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})

```{r define_functions}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
                                                        exp(-eta3*(x-y))))})

model3_fn <- list(alpha.fun = function(x,y,eta1,eta2){return(eta1*x*y*exp(-eta2*abs(x-y)))},
                  q1.fun = function(x,y,eta3){return(exp(-eta3*x))},
                  q0.fun = function(x,y,eta3){return(exp(-eta3*y))})

```{r creat colour df}
col_df <- tibble(method = c("I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
            "C-HP", "C-DCHP", "True", "C-MMHP"),
            cols = viridis(9))

@@

```{r fig-2a-contour-plot}
current_cohort <- 5
#png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x,y){
  return(x*y*eta1_mean*exp(-eta2_mean*abs(x-y))/(1+exp(-eta3_mean*(y-x))))
  # this is because axes are flipped that we have y-x in last term
  #return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(seq(1,0,-0.01),  
                seq(0,1,0.01), 
                z.func)
my.image.plot(seq(0,1,0.01), seq(0,1,0.01), z_plot,
              xlab=expression(f[j]),ylab=expression(f[i]),
              my.main="(a)", cex.main=2.3, 
              cex.lab=2.5, xLabels=c(1,0), yLabels=c(0,1))

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
# current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f,2,mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
                   observe=list(observe.id),
                   observe.length=list(observe.time),
                   no.events=list(no.events))
unique_observe_win <- unique(return_df[,c("observe.id","observe.time")])

ks.stat.matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
n_matrix <- matrix(0,ncol=mice_number,nrow=mice_number)
Lambda_matrix <- matrix(list(),nrow=mice_number,ncol=mice_number)
for(k in 1:mice_number){
  for(l in c(1:mice_number)[-k]){
    i<-expert_rank_10[[current_cohort]][k]
    j<-expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator==i&unique_pairs_df$recipient==j)
    if(length(pair)>0){
      param_mean <- list(lambda0=mean(sim_cohort_hp$lambda0),
                         alpha=model1_fn$alpha.fun(f_est[i],
                                                   f_est[j],
                                                   eta1_mean,
                                                   eta2_mean,
                                                   eta3_mean),
                         beta=mean(sim_cohort_hp$beta))
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for(cur in c(1:length(current_window_vec))){ ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator==i&
                                          return_df$recipient == j &
                            return_df$observe.id==cur_win,"event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator==i&
                                        return_df$recipient==j&
                            return_df$observe.id==cur_win,"observe.time"]
        Lambda_vec <- uniHawkesCompensator(object = param_mean,
                              events = c(current_event_time,
                                         current_obs_time))
        all_Lambda <- c(all_Lambda,Lambda_vec)
        n_matrix[i,j] <- n_matrix[i,j] + length(current_event_time)
      }
      if(length(all_Lambda)>0){
        ks.stat.matrix[i,j] <-  ks.test(all_Lambda,"pexp",
                                        rate = 1/mean(all_Lambda))$statistic
        Lambda_matrix[i,j][[1]] <- all_Lambda
      }
    }
  }
}

# png(paste(plot_path,"/diagonsis_model1_",cohort_names[current_cohort],".png",sep=''),
#     width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
#order(as.vector(ks.stat.matrix),method = "")

values <- as.vector(ks.stat.matrix)
sorted_vals <- sort(ks.stat.matrix)
#match(values,sorted_vals)
col.vec.vir <- vir_cols[match(values,sorted_vals)]

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks.stat.matrix[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
           verticals = TRUE, col = "red", lwd = 2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
m1_ks <- ks.stat.matrix
col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
                col.vec = viridis(100))

temp <- cLegend(as.vector(ks.stat.matrix))
#which(temp$x.vec == as.vector(ks.stat.matrix))
## need to adjust this for the legend also.
# image(1, cLegend(as.vector(ks.stat.matrix))$x.vec,
#       matrix(data=cLegend(as.vector(ks.stat.matrix))$x.vec, 
#              ncol=length(cLegend(as.vector(ks.stat.matrix))$x.vec),nrow=1),
#       col=cLegend(as.vector(ks.stat.matrix))$col.vec,
#       xlab="",ylab="",axes=FALSE)
image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="", axes = FALSE)
axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
     cex.axis=2.4)

mtext(text=expert_rank_10[[current_cohort]],
      side = 1, line = 1.8, outer = TRUE, cex = 1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(b)", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)
#dev.off()
```

@@

```{r fig-3a-baseline-rate}
# current_cohort <- 5

load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
gamma_mean <- apply(sim_cohort_dchp$gamma,2,mean)
zeta_mean <- apply(sim_cohort_dchp$zeta,2,mean)

# social matrix plot
latent_social_matrix <- gamma_mean %*%
  t(rep(1,mice_number)) + rep(1,mice_number) %*% t(zeta_mean)

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
                                         expert_rank_10[[current_cohort]]],
                    xLabels=expert_rank_10[[current_cohort]],
                    yLabels=rev(expert_rank_10[[current_cohort]]) )
                    # title = "(a)" )
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
#dev.off()
```
## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison, include=FALSE,eval=FALSE}
# current_cohort <- 5

colors_plot <- col_df %>% filter(method %in% c("C-HP","C-DCHP")) %>%
  pull(cols) 
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_hp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/cohort_dchp_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0,0,2,0), mar = c(3,4,1,1),mgp=c(0,0.5,0))
plot(order(expert_rank_10[[current_cohort]]),
     apply(sim_cohort_hp$f,2,mean),pch=16,cex=1.2,
     #col= "steelblue",
     col = colors_plot[1],
     ylab="",xlab="",
     xlim=c(1,12.5),ylim=c(0,1), xaxt="n", yaxt="n")
segments(order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)-apply(sim_cohort_hp$f,2,sd),
         order(expert_rank_10[[current_cohort]]),
         apply(sim_cohort_hp$f,2,mean)+apply(sim_cohort_hp$f,2,sd),
         #col= add.alpha("steelblue",0.8),lwd=2)
         col = add.alpha(colors_plot[1],0.8), lwd =2)
points(order(expert_rank_10[[current_cohort]])+0.2,
       apply(sim_cohort_dchp$f,2,mean),
       pch=16,cex=1.2,
       col=colors_plot[2])
       #col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)-apply(sim_cohort_dchp$f,2,sd),
         order(expert_rank_10[[current_cohort]])+0.2,
         apply(sim_cohort_dchp$f,2,mean)+apply(sim_cohort_dchp$f,2,sd),
         col= add.alpha(colors_plot[2],0.8),lwd=2)
         #col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW<-1, at=1:12, labels=expert_rank_10[[current_cohort]], cex.axis=1.3, tck=-0.015)
#mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

axis(LEFT <-2, at=seq(0,1,0.2), labels=seq(0,1,0.2), las= HORIZONTAL<-1,
     cex.axis=1.3, tck=-0.015)
mtext(side=1, text="I&SI rank", line=1.8, cex=1.5)
mtext(side=2, text="Latent rank", line=2.4, cex=1.6)
mtext(side=3, text="(b)", line=0.8, cex=1.6, font=2)
legend('bottomleft', legend = c("C-HP", "C-DCHP"),
       pch = c(16, 16), lty = c(1, 1), lwd=c(2,2),
       #col=c("steelblue","goldenrod"),
       col=c(colors_plot[1],colors_plot[2]),
       cex=1.5)
#dev.off()
```

```{r, eval=FALSE, include=FALSE}
par(mar=c(3,3,1,1))
plot(as.vector(n_matrix[n_matrix>0]), as.vector(ks.stat.matrix[n_matrix>0]),
     xlab="", ylab="", pch=16, col="gray", cex= 0.8, xaxt="n", yaxt="n",
     ylim=c(0,0.65))
mtext("Number of events", cex=1.5, side=1, line=1.8)
mtext("K-S statistics", cex=1.5, side=2, line=1.5)
mgp.axis(1,mgp=c(0,0.3,0),at=seq(0,120,10),cex.axis=1,lwd=0,lwd.ticks=0.1)
mgp.axis(2,mgp=c(0,0.1,0),at=seq(-0.2,0.6,0.2),cex.axis=1,lwd=0,lwd.ticks=0.8)
```

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=3.5,fig.width=8}
sim_data_path <- "../output/sims_m3_update/"

@@

m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
#m1_files

@@

for(i in seq_along(m3_files)) {
  load(paste0(sim_data_path,m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, fig.path = "paper_figure/",
  dev = "png", fig.height = 4.5, fig.width = 7,
  warning = FALSE
)

slides_plots <- FALSE
extra_plots <- FALSE

revision_plots <- TRUE
original_plots <- FALSE
### original plots for plots which are no longer needed, 
### revision plots are what required

current_cohort <- 5

@@

library(here)
library(rstan)
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

cohort_names <- paste("cohort", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                      sep = "")
cohort_short_names <- paste("C", c(9, 10, 12, 15, 16, 17, 18, 37, 38, 45),
                            sep = "")
cut_off <- 3
mice_number <- 12
```

```{r load rankings, echo=FALSE, include=FALSE, results='hide', cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for (curr_cohort in fit_cohorts) {
  naive_rank_10[[curr_cohort]] <-
    naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <-
    expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})
```

```{r define_functions, eval=revision_plots, include=FALSE}
model1_fn <- list(alpha.fun = function(x, y, eta1, eta2, eta3) {
  return(eta1 * x * y * exp(-eta2 * abs(x - y)) / (1 +
    exp(-eta3 * (x - y))))
})

model3_fn <- list(
  alpha.fun = function(x, y, eta1, eta2) {
    return(eta1 * x * y * exp(-eta2 * abs(x - y)))
  },
  q1.fun = function(x, y, eta3) {
    return(exp(-eta3 * x))
  },
  q0.fun = function(x, y, eta3) {
    return(exp(-eta3 * y))
  }
)
```

```{r creat colour df, eval=revision_plots, include=FALSE}
col_df <- tibble(
  method = c(
    "I&SI", "AggRank", "DSNL", "Glicko", "I-MMHP",
    "C-HP", "C-DCHP", "True", "C-MMHP"
  ),
  cols = viridis(9)
)
```

@@

```{r fig-2a-contour-plot, eval=revision_plots}
current_cohort <- 5
# png(paste(plot_path,"contour.png",sep=""),width=480,height=480)
load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
z.func <- function(x, y) {
  return(x * y * eta1_mean *
           exp(-eta2_mean * abs(x - y)) / (1 + exp(-eta3_mean * (y - x))))
  # this is because axes are flipped that we have y-x in last term
  # return(x*y*eta1_mean/(1+exp(eta2_mean*abs(x-y)-eta3_mean*(y-x))))
}
z_plot <- outer(
  seq(1, 0, -0.01),
  seq(0, 1, 0.01),
  z.func
)
my.image.plot(seq(0, 1, 0.01), seq(0, 1, 0.01), z_plot,
  xlab = expression(f[j]), ylab = expression(f[i]),
  my.main = "(a)", cex.main = 2.3,
  cex.lab = 2.5, xLabels = c(1, 0), yLabels = c(0, 1)
)
```

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE, eval=revision_plots}
# current_cohort <- 5

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_hp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
eta1_mean <- mean(sim_cohort_hp$eta_1)
eta2_mean <- mean(sim_cohort_hp$eta_2)
eta3_mean <- mean(sim_cohort_hp$eta_3)
f_est <- apply(sim_cohort_hp$f, 2, mean)
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort,
  raw_df =
    full_data[[cohort_names[current_cohort]]],
  clean_data
)
unique_pairs_df <- return_df %>%
  group_by(initiator, recipient) %>%
  dplyr::summarize(
    count = n(),
    observe = list(observe.id),
    observe.length = list(observe.time),
    no.events = list(no.events)
  )
unique_observe_win <- unique(return_df[, c("observe.id", "observe.time")])

ks.stat.matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
n_matrix <- matrix(0, ncol = mice_number, nrow = mice_number)
Lambda_matrix <- matrix(list(), nrow = mice_number, ncol = mice_number)
for (k in 1:mice_number) {
  for (l in c(1:mice_number)[-k]) {
    i <- expert_rank_10[[current_cohort]][k]
    j <- expert_rank_10[[current_cohort]][l]
    pair <- which(unique_pairs_df$initiator == i & 
                    unique_pairs_df$recipient == j)
    if (length(pair) > 0) {
      param_mean <- list(
        lambda0 = mean(sim_cohort_hp$lambda0),
        alpha = model1_fn$alpha.fun(
          f_est[i],
          f_est[j],
          eta1_mean,
          eta2_mean,
          eta3_mean
        ),
        beta = mean(sim_cohort_hp$beta)
      )
      current_window_vec <- unique_pairs_df$observe[[pair]]
      all_Lambda <- numeric(0)
      for (cur in c(1:length(current_window_vec))) { ## check length > 2
        cur_win <- current_window_vec[cur]
        current_event_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "event.times"][[1]]
        current_obs_time <- return_df[return_df$initiator == i &
          return_df$recipient == j &
          return_df$observe.id == cur_win, "observe.time"]
        Lambda_vec <- uniHawkesCompensator(
          object = param_mean,
          events = c(
            current_event_time,
            current_obs_time
          )
        )
        all_Lambda <- c(all_Lambda, Lambda_vec)
        n_matrix[i, j] <- n_matrix[i, j] + length(current_event_time)
      }
      if (length(all_Lambda) > 0) {
        ks.stat.matrix[i, j] <- ks.test(all_Lambda, "pexp",
          rate = 1 / mean(all_Lambda)
        )$statistic
        Lambda_matrix[i, j][[1]] <- all_Lambda
      }
    }
  }
}
#
# png(paste(plot_path,
#           "/diagonsis_model1_",
#           cohort_names[current_cohort],
#           ".png",
#           sep = ''),
#     width=480,height=480)
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks.stat.matrix))
# need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks.stat.matrix))))
# order(as.vector(ks.stat.matrix),method = "")

values <- as.vector(ks.stat.matrix)
sorted_vals <- sort(ks.stat.matrix)
# match(values,sorted_vals)
col.vec.vir <- vir_cols[match(values, sorted_vals)]

####
par(
  oma = c(6, 4, 4, 1), mar = rep(0, 4),
  mgp = c(0, .2, 0)
)
layout(cbind(matrix(
  data = c(1:(12 * 12)), nrow = 12, ncol = 12,
  byrow = TRUE
), rep(12 * 12 + 1, 12)),
widths = c(rep(1, 12), 2), heights = rep(1, 12)
)
for (i in expert_rank_10[[current_cohort]]) {
  for (j in expert_rank_10[[current_cohort]]) {
    if (ks.stat.matrix[i, j] == 0) {
      plot(0, 0,
        xlim = c(0, 5), ylim = c(0, 5), type = "n", xlab = "", ylab = "",
        axes = FALSE, frame = TRUE
      )
      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
        border = 0, col = "white"
      )
    } else {
      Lambda.test <- Lambda_matrix[i, j][[1]]
      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
        ylab = "", xlab = "", axes = FALSE, frame = TRUE
      )
      rect(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[4],
        border = 0, col = col.vec.vir[matrixToVecIdx(i, j, mice_number)]
      )
      curve(pexp(x, 1 / mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
        ylab = "", xlab = "", axes = FALSE, frame = TRUE, add = TRUE, lwd = 2
      )
      plot(ecdf(Lambda.test),
        add = TRUE, do.points = FALSE,
        verticals = TRUE, col = "red", lwd = 2
      )
    }
  }
}
par(mar = c(0, 2, 0, 3), mgp = c(0, 0.8, 0))
m1_ks <- ks.stat.matrix
col_obj <- list(
  x.vec = seq(0, max(as.vector(ks.stat.matrix)), length.out = 100),
  col.vec = viridis(100)
)

temp <- cLegend(as.vector(ks.stat.matrix))
# which(temp$x.vec == as.vector(ks.stat.matrix))
## need to adjust this for the legend also.
# image(1, cLegend(as.vector(ks.stat.matrix))$x.vec,
#       matrix(data=cLegend(as.vector(ks.stat.matrix))$x.vec,
#              ncol=length(cLegend(as.vector(ks.stat.matrix))$x.vec),nrow=1),
#       col=cLegend(as.vector(ks.stat.matrix))$col.vec,
#       xlab="",ylab="",axes=FALSE)
image(1, col_obj$x.vec,
  matrix(
    data = col_obj$x.vec,
    ncol = length(col_obj$x.vec), nrow = 1
  ),
  col = col_obj$col.vec,
  xlab = "", ylab = "", axes = FALSE
)
axis(4,
  at = c(0, 0.3, 0.6), labels = c(0, 0.3, 0.6), las = HORIZONTAL <- 1,
  cex.axis = 2.4
)

mtext(
  text = expert_rank_10[[current_cohort]],
  side = 1, line = 1.8, outer = TRUE, cex = 1.8,
  at = 1 / 14 * c(1:12) - 1 / 22
)
mtext(
  text = expert_rank_10[[current_cohort]],
  side = 2, line = 0.5, outer = TRUE, cex = 1.8,
  at = 1 / 12 * c(12:1) - 1 / 20, las = 2
)
mtext(
  text = "(b)", side = 3, line = 1.4, outer = TRUE,
  cex = 2.2,
  at = 0.45, font = 2
)
# dev.off()
```

@@

```{r fig-3a-baseline-rate, eval=revision_plots}
# current_cohort <- 5

load(paste(data_path, cohort_names[current_cohort],
  "/cohort_dchp_stan_result_", cohort_names[current_cohort],
  ".RData",
  sep = ""
))
gamma_mean <- apply(sim_cohort_dchp$gamma, 2, mean)
zeta_mean <- apply(sim_cohort_dchp$zeta, 2, mean)

# social matrix plot
latent_social_matrix <- gamma_mean %*%
  t(rep(1, mice_number)) + rep(1, mice_number) %*% t(zeta_mean)

# png(paste(plot_path,"/lambda0_",
# cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
matrixPlotParameter(latent_social_matrix[
  rev(expert_rank_10[[current_cohort]]),
  expert_rank_10[[current_cohort]]
],
xLabels = expert_rank_10[[current_cohort]],
yLabels = rev(expert_rank_10[[current_cohort]])
)
# title = "(a)" )
# mtext(text=c(1,2,11,6,7,9), side=1, line=-0.35, outer=TRUE, cex=1.3,
#       at=1/17.8*seq(2,12,2)+0.09)
# dev.off()
```

## Figure 3b: Ranking Comparison

```{r fig-3b-rank-comparison, include=FALSE,eval=original_plots}
# current_cohort <- 5
colors_plot <- col_df %>%
  filter(method %in% c("C-HP", "C-DCHP")) %>%
  pull(cols)
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_hp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
load(paste(data_path,
  cohort_names[current_cohort],
  "/cohort_dchp_stan_result_",
  cohort_names[current_cohort],
  ".RData",
  sep = ""
))
# png(paste(plot_path,"/rank_",cohort_names[current_cohort],".png",sep=''),
#     width=400, height=300)
par(oma = c(0, 0, 2, 0), mar = c(3, 4, 1, 1), mgp = c(0, 0.5, 0))
plot(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean),
  pch = 16, cex = 1.2,
  # col= "steelblue",
  col = colors_plot[1],
  ylab = "", xlab = "",
  xlim = c(1, 12.5), ylim = c(0, 1),
  xaxt = "n", yaxt = "n"
)
segments(order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) -
    apply(sim_cohort_hp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]),
  apply(sim_cohort_hp$f, 2, mean) +
    apply(sim_cohort_hp$f, 2, sd),
  # col= add.alpha("steelblue",0.8),lwd=2)
  col = add.alpha(colors_plot[1], 0.8), lwd = 2
)
points(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean),
  pch = 16,
  cex = 1.2,
  col = colors_plot[2]
)
# col="goldenrod2")
segments(order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) - apply(sim_cohort_dchp$f, 2, sd),
  order(expert_rank_10[[current_cohort]]) + 0.2,
  apply(sim_cohort_dchp$f, 2, mean) + apply(sim_cohort_dchp$f, 2, sd),
  col = add.alpha(colors_plot[2], 0.8), lwd = 2
)
# col= add.alpha("goldenrod2",0.8),lwd=2)

axis(BELOW <- 1, at = 1:12, 
     labels = expert_rank_10[[current_cohort]],
     cex.axis = 1.3,
     tck = -0.015)
# mtext(text=11, side=1, line=0.5, cex=1.3, at=6)

axis(LEFT <- 2,
  at = seq(0, 1, 0.2), labels = seq(0, 1, 0.2), las = HORIZONTAL <- 1,
  cex.axis = 1.3, tck = -0.015
)
mtext(side = 1, text = "I&SI rank", line = 1.8, cex = 1.5)
mtext(side = 2, text = "Latent rank", line = 2.4, cex = 1.6)
mtext(side = 3, text = "(b)", line = 0.8, cex = 1.6, font = 2)
legend("bottomleft",
  legend = c("C-HP", "C-DCHP"),
  pch = c(16, 16), lty = c(1, 1), lwd = c(2, 2),
  # col=c("steelblue","goldenrod"),
  col = c(colors_plot[1], colors_plot[2]),
  cex = 1.5
)
# dev.off()
```

```{r, eval=FALSE, include=FALSE}
## need Hmisc for this

par(mar = c(3, 3, 1, 1))
plot(as.vector(n_matrix[n_matrix > 0]),
     as.vector(ks.stat.matrix[n_matrix > 0]),
     xlab = "",
     ylab = "",
     pch = 16,
     col = "gray",
     cex = 0.8,
     xaxt = "n",
     yaxt = "n",
  ylim = c(0, 0.65)
)
mtext("Number of events", cex = 1.5, side = 1, line = 1.8)
mtext("K-S statistics", cex = 1.5, side = 2, line = 1.5)
mgp.axis(1, mgp = c(0, 0.3, 0),
         at = seq(0, 120, 10),
         cex.axis = 1,
         lwd = 0,
         lwd.ticks = 0.1)
mgp.axis(2, mgp = c(0, 0.1, 0),
         at = seq(-0.2, 0.6, 0.2),
         cex.axis = 1,
         lwd = 0,
         lwd.ticks = 0.8)
```

@@

## Figure 4a Recover Latent Ranks
```{r fig-4a, fig.height=3.5, fig.width=8, eval=original_plots}
sim_data_path <- "../output/sims_m3_update/"

@@

m3_files <- list.files(sim_data_path, pattern = "sim_model3_fit*")
# m1_files

@@

for (i in seq_along(m3_files)) {
  load(paste0(sim_data_path, m3_files[i]))
  sim_model3_stan_sim1_total[[i]] <- sim_model3_stan_sim1
  sim_model3_stan_sim2_total[[i]] <- sim_model3_stan_sim2
  sim_model3_stan_sim3_total[[i]] <- sim_model3_stan_sim3
}

# png(paste(plot_path,"sim_latent_recover.png",sep=""), height=500, width=900)
par(
  mfrow = c(3, length(object_par$f_vec_1)),
  mar = c(0, 0, 1, 0),
  oma = c(6.5, 11, 3.5, 1)
)

y.ub <- c(12, 12, 12, 12, 12)
text.y <- c(rep(8, 4), 8)
text.x <- c(0.1, 0.2, 0.4, 0.7, 0.9)
text.x.adj <- c(0.3, 0.4, 0.6, 0.5, 0.8)

model_colors <- col_df %>%
  filter(method %in% c(
    "C-HP",
    "C-DCHP", "C-MMHP"
  )) %>%
  pull(cols)
